### 2022-08-09 paper/Chapters/Chapter01.tex
update paper

%% main problem, introduce deep learning, UNet
In 3D computer vision tasks, the \textit{point cloud} ( i.e. a great number of point positions on the object surface, these numbers of points altogether, are called point cloud) is a common input data to describe the object surface. Based on the geometry information containing in the point cloud, we can acquire the corresponding surface normal, which is an importance features in computer vision, and it can be further used for surface reconstruction, shadings generation and other visual effects. A common approach to acquire the surface normal from the point cloud is the optimization approach which consider the neighbor points in the same plane and calculate the plane normal. However, for the single input data with only one shot recording, like the depth camera, the acquired point cloud is converted from depth map. But due to the optical noises and the reflections in dark and shiny areas of the object surface, the depth map is usually semi-dense only. Thus it limited the neighbor based approach since the missing data leads to fewer neighbors of each point. However, recent advances in image inpainting areas have motivated researchers to recover the missing regions in the input data using deep neural networks and achieves a good performance. For example, \cite{gconv} uses a gated convolution network to inpaint a custom removed areas in the images. \cite{nconv} uses normalized convolution network to enhance the semi-dense depth map to fully dense depth map. Either work takes in-complete input data and mends it to fully dense output. Thus a deep learning based approach can be a way to deal with the semi-dense depth map input for surface normal estimation task.

\begin{figure}[h!]
	\centering
	{\includegraphics[width=.45\textwidth]{./Figures/point-cloud.png}}
	{\includegraphics[width=.45\textwidth]{./Figures/point-cloud-zoom-in.png}}
	\decoRule
	\caption{Left: A piece of point cloud of the dragon object. Right: Zoom in of the point cloud.}
	\label{fig:point-cloud}
\end{figure}

%% introduce photometric stereo
Photometric stereo is another approach in computer vision which can be used for surface normal estimation, where the normals are inferred from appearance variations under multiple illuminations. The relative methods are typically solve the least square problem based on the point-wise image formation model.\cite{SFS} and based on the Bidirectional Reflectance Distribution Function (BRDF). While BRDF based model generally cannot account the global illumination effects and this is usually an unavoidable problem due to the light interactions and difficult traced mathematically.

%% papers contribution, main work
Both directions mentioned above have been widely researched using deep learning approaches. However, the approach that takes both geometry and illuminated information together into account for normal estimation remains impoverishment. We present a deep learning based approach takes both geometry and photometric information into account for normal inference. For a practical reason, we consider only 1 illuminated image based on the calibrated camera and takes semi-dense point cloud as input data. To achieve this goal, we will mainly take the geometry information into consideration and take the photometric information as a supplementary.

%% introduce the network, trip-net, dataset
One of our challenges is to apply the semi-dense input data to the neural network in an image-wise way. UNet is a good network applying for computer vision tasks with up-sampling requirements. We modified it with a gated activation unit called \textit{gated convolution layer (gconv)} to handle semi-dense input data. Another challenge is to merge the different input data feature maps to cooperatively improved the surface normal inference task. We propose a $ multi-fusion $ scheme for integration on separate feature map extractors. We will show that this multi-fusion design can be taken advantage of by a combination of different input data types and improved surface normal inference performance. To train our network, we create a synthetic RGB-D image dataset by utilizing one light source illumination and one ambient light illumination to simulate application scenarios. To simulate depth maps in the real world, we applied uniform distributed drop-out noise to the input data with a control parameter for noise density.

%% experiments
We trained our approach on our proposed synthetic dataset ``synthetic-50-5" and evaluate it on 6 different metrics. We compare our approach against the geometry information based approach based on similar network architecture and show that our calibrated illuminated RGB-D image based approach further improved normal accuracy. We also applied our model to a real dataset and compare it with the optimization based approach.

The structure of the thesis is as follows, Chapter 1 is the introduction of the whole work. Chapter 2 briefly discusses the related work about normal inference. Chapter 3 is the main approach of this work. Chapter 4 introduces the created dataset for the training work. Chapter 5 is the description of the experiments and the evaluation of the models. Chapter 6 is the conclusion of the whole thesis.

>>>>

%% main problem, introduce deep learning, UNet

In 3D computer vision tasks, the \textit{point cloud} (i.e., an unstructured set of 3D points representing the surfaces in the scene) is a common input file to describe the object surface. Based on the geometry information in the point cloud, we can calculate the corresponding surface normal, which is an important feature in computer vision. The surface normal can be used for surface reconstruction, shading generation and other visual effects. The common method for determining the surface normal from the point cloud is the optimization approach, which considers the neighboring points in the same plane and calculates the surface normal.

However, for single input data with only one shot, such as the data acquired by a depth camera, the point cloud is converted from a depth map and the given calibration information. In the case of active depth sensors, the depth map is usually only semi-dense due to optical noise and reflections in dark and shiny areas of the object surface, missing many pixels and holes. This limits the neighborhood-based approach because the missing data results in a smaller number of neighbors for each point. However, recent advances in the field of image inpainting have motivated researchers to use deep neural networks to recover the missing regions in the input data and achieve good performance. For example, \cite{gconv} uses a gated convolution network to recover user-defined removed regions in the images. \cite{nconv} uses a normalized convolution network to extend the semi-dense depth map to a fully dense depth map. In both cases, incomplete input data is used and converted to a fully dense output. Therefore, a Deep Learning based approach can be a way to deal with semi-dense depth maps for surface normal estimation tasks.

\begin{figure}[h!]
	\centering
	\captionsetup{width=\linewidth}
	{\includegraphics[width=.49\textwidth]{./Figures/point-cloud.png}}
	{\includegraphics[width=.49\textwidth]{./Figures/point-cloud-zoom-in.png}}
	\decoRule
	\caption{Left: A portion of the point cloud of the \textit{dragon} object. Right: Zoom in of the point cloud.}
	\label{fig:point-cloud}
\end{figure}

%% introduce photometric stereo
Photometric stereo is another approach in computer vision that can be used for estimating surface normals, where the normals are derived from appearance variations under different illuminations. The corresponding methods are usually solved using the least squares problem, which is based on the point-wise image formation model \cite{SFS} and on the assumption of the Lambert surface. However, the Lambert surface generally cannot account for global illumination effects, which is an unavoidable problem due to light interactions.

%% papers contribution, main work
Both of the above directions have been widely explored using deep learning approaches. However, the approach that considers both geometry and illuminated information for normal estimation remains insufficient. We present a Deep Learning based approach that considers both geometric and photometric information for normal inference. For practical reasons, we consider a semi-dense depth map with only one additional illuminated image based on the calibrated camera as input data to find a compromise between the two methods.

%% introduce the network, trip-net, dataset
One of our challenges is to apply the semi-dense input data to the neural network in an image-aware manner. \textit{U-Net} is a good network for computer vision tasks with up-sampling requirements. We modified it with a gated activation unit called \textit{gated convolution layer (gconv)} to handle semi-dense input data. Another challenge is to merge the different feature maps of the input data to cooperatively improve the surface normal inference task. We propose a \textit{multi-fusion} scheme for integrating separate feature maps. We will show that this \textit{multi-fusion} design can be leveraged by combining different input data types and improving the performance of surface normal inference. To train our network, we create a synthetic RGB-D image dataset by using a light source and ambient light illumination to simulate application scenarios. To simulate depth maps in the real world, we added uniformly distributed drop-out noise to the input data, with the noise density controlled by a parameter.

%% experiments
We trained our models on our proposed synthetic dataset \textit{synthetic-50-5} and evaluated them on 6 different metrics. The results show that our approach based on calibrated illuminated RGB-D images further improves the normal accuracy. We also applied our model to a real dataset and compared it with the optimization-based approach.

The structure of the paper is as follows: In Chapter 2, we briefly discuss related work on the normal inference task. Chapter 3 briefly introduces a traditional optimization-based approach and photometric stereo, and then proposes two learning-based approaches for surface normal estimation. Chapter 4 presents the dataset created for the training work and its preprocessing. Chapter 5 analyzes the experiments and provides both qualitative and quantitative evaluations of the models. Chapter 6 is the summary of the entire thesis.

### 2022-08-09 paper/Chapters/Chapter02.tex
update paper

%% depth map approach
Surface normal inference is a widely researched topic and can be solved in multiple directions. Based on a structured point cloud, the surface normal can be derived from geometry information of the point cloud, which mainly utilizes the neighbor information and consider it as an optimization problem (\cite{optimized-methods} ). They can perform well on dense point cloud input data based on a well-chosen window size. However, the drawbacks are that the algorithms are highly noise sensitive. 
The point cloud is usually not fully dense and normally converted from depth map, which are usually with missing pixels and holes on dark, shinny or transparent regions (\cite{nyu}). The missing points destabilizes the geometry based solution. To ease this problem, \cite{Holzer.S} proposed method to use local neighbors with an interest parameter $ p $ and compute the eigenvectors of the corresponding covariance matrix, which is used to smooth the depth data in order to handle the noise of depth image.  \cite{depth-inpainting-distribution} proposed an approach considers the depth distributions of neighboring regions to fill the holes in the depth map. 
Some approaches use deep learning method to fill missing areas. \cite{nconv} introduces normalized convolution to deal with missing or uncertain depth data with an added mask on the standard convolution operation. \cite{ncnn} applied it and use it as normalized convolution layers in their networks, which aims to reconstruct the missing pixels from the sparse depth map sensed by cameras. \cite{pncnn} proposed an input confidence estimation network to estimate the confidence instead of using a binary mask.

%% photometric approach
Photometric stereo is another approach that infer surface normal from BRDF based surface model. The surface normal is related with observed intensity, the incoming light direction, the outgoing viewing direction and the light intensity. It required multiple light conditions to get an optimal solution.

%% fusion approach

%% talk about gated convolution, Unet

%% in summary

\paragraph{Unstructured Point Cloud Based}
For the unstructured point cloud, the neighbor information of each point is usually unknown. K-nearest neighbor (KNN) is a common algorithm for neighbor searching. With knowing this information, the neighbor based approaches can be used as a second step. However, KNN-method merely based on the Euclidean distance in the 3D space. Therefore, the points of the other surfaces but in a close distance will also be considered as neighbors. To ease this problem, \cite{unstructed-pc} proposed a method based on unstructured point cloud with selecting the optimal scale around each point for normal estimation. To calculate the normals of multiple points in parallel \cite{unstructed-pc-patch-stitching} processes a series of overlapping patches for normal estimation.

Deep learning based methods take single RGB image or RGB-D image as the input for normal estimation. It has a strong relationship with the depth inference tasks, two benchmarks are highly used in these area. (\cite{nyu} and \cite{kitti-depth}) Based on the input of training model, the methods can be roughly divided as follows:

\paragraph{RGB based} RGB based methods predict the depth map diretly from single RGB image.
\cite{Eigen} proposed a two staged network for depth map prediction based on RGB image, which consider the global features and the local features respectively. \cite{img2depth} employed Residual Network for the feature extraction and further designed a upsampling part which replace the fully-connected layer with the unpolling layers. 
\cite{geometry_based_solution} proposed a method to learn discriminative and geometrically informative primitives from RGBD images, which is further used to recover the surface normals of a scene from a single image. 
\cite{GeoNet} uses ResNet (\cite{resnet}) to infer a coarse surface normal based on RGB image, and further refine it with the help of depth map based on the methods based on \cite{geometry_based_solution}. \cite{binsformer} proposed a method achieved state of art in NYUv2 Dataset (\cite{nyu}), which adaptively generate information to predict depth maps based on RGB image.

\paragraph{RGB-D based}
\cite{hfm} based on UNet architecture for normal estimation using RGB-D image as input. The RGB image and depth map are in the separate branches and imply a fusion module in four sections of the network to concatenate two branches. It also considers the confidence of the values in depth map.

\cite{depth-enhance-guided} further integrated RGB image as the guidance to deal with the missing pixels in the depth map.

>>>>

Surface normal inference is a widely researched topic and can be solved in several ways. Traditionally, it can be derived from a point cloud. There are many optimization-based approaches to computing surface normals pixel-by-pixel using neighborhood information. \cite{optimized-methods} gives a comparison between some of these approaches. \cite{Holzer.S} proposed a method of using local neighbors with an interest parameter $ p $ and derives the surface normal from the eigenvectors of the corresponding covariance matrix. These approaches work well for dense input data based on a well-chosen window size.
However, in many practical datasets such as NYU Depth Dataset V2 \cite{nyu} and KITTI-Depth\cite{kitti-depth}, the point clouds are often converted from depth maps.
But the depth maps are usually very noisy and contains many missing pixels and holes in dark, shiny, or transparent areas. This poses more of a challenge for neighborhood-based approaches, as neighborhood information is not available in many of these areas.

To solve this problem, some approaches focus on improving the depth map by estimating missing regions. \cite{depth-inpainting-distribution} proposed an approach that considers the depth distributions of neighboring regions to fill the holes in the depth map. \cite{ncnn} uses a deep learning-based approach for painting semi-dense depth maps, which mainly uses the normalized convolution proposed by \cite{nconv}. This approach considers a 0-1 mask to distinguish valid and invalid data points. \cite{pncnn} improved this approach by proposing an input confidence estimation network to replace the binary mask with an estimated confidence mask. \cite{depth-enhance-guided} also uses a normalized convolution for inpainting the depth map and also uses an RGB image as a guidance.

On the other hand, some of the approaches use RGB-D images to estimate the surface normal or use RGB images to estimate the fully dense depth map.
\cite{Eigen} proposed a two-level network for predicting the depth map based on RGB images, where the global and local features of the object are considered separately. \cite{img2depth} also predicts the depth map from the image, using a residual network for feature extraction and developing an up-sampling part with the un-polling layers. 
\cite{binsformer} proposed a method that adaptively generates depth map prediction information based on RGB images. 
\cite{geometry_based_solution} uses RGB-D images to estimate surface normals. It proposes a method for learning discriminative and geometrically informative primitives from RGB-D images, which is then used to recover the surface normals of a scene from a single image. 
\cite{GeoNet} uses ResNet \cite{resnet} to derive a coarse surface normal from an RGB image, and refines it using a depth map based on the \cite{geometry_based_solution} method. 
\cite{hfm} derives surface normals based on an RGB-D image using the \textit{U-Net} architecture.

However, these approaches mainly rely on RGB images as input for estimating the normal or the full depth map. The applied scenarios are mainly indoor scenes such as bedrooms or offices, where the focus is not on the fine details of the object surface, but only on the main directions of each area, such as the directions of the floor, walls, or seats, etc as shown in Figure \ref{fig:dataset-comparison}

\begin{figure}[h!]
	\centering
	\captionsetup{width=\linewidth}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/nyu_depth_v2_img.jpg}
		\caption{}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
	\includegraphics[width=\linewidth]{./Figures/nyu_depth_v2_depth.jpg}
	\caption{}
\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
	\includegraphics[width=\linewidth]{./Figures/train-image.png}
	\caption{}
\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
	\includegraphics[width=\linewidth]{./Figures/train-depth-noise.png}
	\caption{}
\end{subfigure}
	\decoRule
	\caption{(a)-(b): Output from the RGB camera (a) and depth camera (b) of a scene in \textit{NYU Depth Dataset V2} \cite{nyu}. (c)-(d): Output from the gray-scale camera (c) and depth camera (d) of a scene in our proposed dataset \textit{synthetic-50-5}.}
	\label{fig:dataset-comparison}
\end{figure}
%% Photometric Stereo
Photometric stereo is another approach that derives the surface normal from the BRDF-based surface model. The surface normal is related to the observed intensity, the direction of incident light, the direction of outgoing light, and the light intensity. Several light conditions are required to obtain an optimal solution. \cite{CNN-PS} uses a CNN-based approach to learn the relationship between photometric stereo input and the surface normal under hundreds of lighting conditions, which is also robust to the effects of global illuminations. \cite{spline-net} is based on an illumination interpolation network to use only a sparse set of lights for photometric stereo tasks.

Our approach uses an RGB-D image but known light direction and calibrated information for surface normal inference, which considers multiple input data types into account for the estimation.

### 2022-08-09 paper/Chapters/Chapter04.tex
update paper

\section{Resource}
The object model we used are searched from internet.
A set of point cloud datasets for computer vision research has been published by /cite[data1], /cite[data2], /cite[data3] and /cite[data4]. These point clouds are scanned from real objects using high resolution scanners like Cyberware 3030 MS+ and calibrated with post processing. All objects has been scanned for hundreds of times with an exhaustive completion for the origin objects, which is up to millions points. (\cite{data1}). The dense point clouds make the normal inference task trivial since the neighbor based method performs adequately for this kind of task. Some of the point clouds even contain pre-computed normal maps based on more advanced methods. They all provide the accurate ground truth for the supervised learning method.

@@

	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/08.pergolesi-side-chair_texture.png}
		\caption{chair}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/42.zebra_texture.png}
		\caption{zebra}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test-dataset/01.bus_texture.png}
		\caption{bus}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test-dataset/03.baoshanlu_texture.png}
		\caption{baoshanlu}
	\end{subfigure}
	\decoRule
	\label{fig:dataset-demo}
	\caption{Point clouds scanned by high resolution scanners}
\end{figure}
Besides, some objects also have colored textures, as shown in the second row of Figure \ref{fig:dataset-demo}. This is specially prepared for the illuminated approach since they will take the image into account to evaluate the surface normal. By using textured models, our models become closer to the real dataset and have improved robustness, which can apply to the real dataset further.

\definecolor{direction-light-color}{RGB}{255,244,214}
\newcommand{\col}[1]{%
	\textcolor{#1}{\vrule width 0.5cm}}
\section{Synthesize Scenes using Unity}
In order to simulate the data collection scenario close to the real world as much as possible. We did the following settings. A flat cylinder called $ stage $ is placed in the center of the 3D space as a platform to place objects. We fixed the stage in a predetermined position, which is not changed when images are captured. 
To provide ambient light, one directional light with RGB color FFF4D6 /col[direction-light-color] is placed in a top-view direction at a distance of 25 meters, which also has a fixed location.
An RGB-D camera is placed in a top-view direction around 10m away from the stage. The camera captures the depth map and the gray-scale image, which is randomly arranged after each scene. The moving range of the camera has 0.1m in both directions of the X, Y, and Z axis and a 1-degree random changed Euler angle. 
As an illumination light, a point light is placed around 5 meters away, which is also randomly moved after each scene. The moving range is 0.3m in both directions of the X, Y, and Z axis and 1 degree random in the Euler angle.

@@

\section{Data preprocessing}
The raw data captured from Unity required further preprocessing before feeding them into the training models. 
A depth map is captured by a depth camera in Unity, which is a 1 channel image that contains information relating to the distance of the surfaces of the scene objects from a viewpoint. It can be saved as a 16-bit gray-scale image, i.e. each pixel in the range $0 - 65535$.

The gray-scale image can be used as a guided normal inference task and also as a readable scene for humans. Since the image captured by the camera is in RGB format, we need to convert it to gray colors for our models. It is based on the following equation.
\[ gray: \frac{R+2G+B}{4}  \]

The normal map is the tangent surface normal, which is saved in a 32-bit RGB color image. The surface normal $ (n_x, n_y, n_z) $ and its corresponding RGB color $ (R,G,B) $ can be converted based on the following equation:
\begin{dgroup*}
	\begin{dmath*}
		n_x = \frac{R}{255} * 2 - 1
	\end{dmath*}
	\begin{dmath*}
		n_y = \frac{G}{255}*2 - 1
	\end{dmath*} 
	\begin{dmath*}
		n_z = 1-\frac{B}{255} * 2
	\end{dmath*}
\end{dgroup*}

If consider the relation between Lambertian reflection and normal direction, the light source can be used to calculate the reflect direction of each point.

The camera intrinsic and extrinsic matrix helps point cloud calculation.

\subsection{Convert to Point Cloud}
\label{sec:depth-map-to-point-cloud}

The depth map can be converted to a 3D vertex point cloud as the input of the normal inference model.

\begin{figure}[h!]
	\centering
	\begin{tikzpicture} 
		% reference lines
		\draw[thick,dashed]	(0,0) -- (10,0) ; % bottom
		\draw[thick,dashed]	(0,3) -- (10,3) node[pos=0.9, above] {image plane}; % middle
		\draw[thick,dashed]	(0,6) -- (10,6); % top
		% camera 
		\filldraw[black] (5,0) circle (2pt) node[anchor=south west]{Camera Position};
		% world point 
		\filldraw[black] (7,6) circle (2pt) node[anchor=north west]{Point};
		% image point
		\filldraw[black] (6,3) circle (2pt) node[anchor=north west]{Pixel};
		% similiar triangles
		\draw[thick] (5,0) -- (5,6); % AB
		\draw[thick] (5,0) -- (7,6); % AC
		\draw[thick] (5,6) -- (7,6) node[midway, below] {$ X $}; % BC
		\draw[thick] (5,3) -- (6,3) node[midway, below] {$ u $};
		% measure arrows
		\draw[thick, <->] (4,0) -- (4,3) node[midway, left] {$ fk_u $};
		\draw[thick, <->] (3,0) -- (3,6) node[pos=0.3, left] {$ Z $};
	\end{tikzpicture}	
	\decoRule
	\caption{Convert depth to point in camera coordinate system}
	\label{fig:depth-triangulation}
\end{figure}

Consider a 3-dimensional Euclidean space. Use $ z $ axis to denote the depth. The $ x  $ and $ y $ axis are perpendicular to each other. For a pixel $ (u,v) $ on depth map, its depth $ D(u,v) $ is the $ Z $ component of the corresponding point $P_C = (X,Y,Z) $ regarding camera coordinate system. The $ X $ and $ Y $ can be calculated based on the triangle similarity.
\begin{dgroup*}

	\begin{dmath*}
		X = \frac{uZ}{fk_u}
	\end{dmath*}
	\begin{dmath*}
		Y = \frac{vZ}{fk_v}
	\end{dmath*}
\end{dgroup*}
where $ fk_u, fk_v $ is the focal length in pixels align $ u $ and $ v $ axes.
Converted a point from camera coordinate system to the world coordinate system, using extrinsic matrix $ R $ and $ t $
\[P_W = P_CR+t \]

\subsection{Point Cloud Normalization}
\label{sec:dataset-normalization}
%% How to represent input tensor, to make it fast converse
The sizes of each training object are various, whereas it should be as an invariant value for the training model. Thus normalization is required before feeding training objects into the models.
We showed the data fluctuation in each axis in Figure \ref{fig:data-range}. Table \ref{tab:data-range} gives a quantitative evaluation of the corresponding average values.

@@

\begin{dmath*}
	s = \max(X)-\min(X)
\end{dmath*}
It is calculated as the range of the $ X $ axis, but theoretically can be used by the $ Y $ or $ Z $ axes as well.

\begin{figure}[!h]
	\centering
	{\includegraphics[width=0.45\textwidth]{./Figures/Data_Extreme.png}}
	{\includegraphics[width=0.45\textwidth]{./Figures/Data_Range.png}}
	\label{fig:data_range}
	\decoRule
	\caption{Left: Extreme value in 3 axis; Right: Vertex range in 3 axis}
\end{figure}

\begin{table}[th]
	\label{tab:data-range}
	\centering
	\begin{tabular}{c | c c c}
		\toprule
		\tabhead{Axis} & \tabhead{Scale} & \tabhead{Min} & \tabhead{Max}\\
		\midrule
		X & 1.48 & -0.75 & 0.73\\
		\hline 
		Y & 1.56 & -0.76 & 0.80\\
		\hline 
		Z & 1.47 & 6.53 & 8.00\\
		\bottomrule

	\end{tabular}
	\caption{ The fluctuation of extreme values and their ranges in 100 random training items. }
\end{table}

\subsection{Noise}
\label{sec:noise}
The raw depth maps captured by light scanners usually have missing pixels. In order to fit well with real data, the synthetic data has been added uniform distributed noise, which randomly removes the valid pixels in the maps.
The simulated noise is distributed evenly around the whole map with specific noise intensity. A parameter $ \mu $ is used to control the intensity of noise. It denotes the $ \mu $-percent pixel drop-off. For example, $ \mu-10 $ removes 10\% pixels randomly. For each scene, the noise operation based on a random $ \mu $ in a range $ \left[0, 50\right]  $ is used. Some scenes have more missing pixels and some have fewer. The random noise intensity also enables the model to learn scenarios not only with noise but also with minor noise or even without noise.
Figure \ref{fig:noise-intensity} shows the noise effect with different $ \mu $.
%% add noise image
\begin{figure}[!h]
	\centering
	{\includegraphics[width=.9\textwidth]{./Figures/add_noise_depth.png}}
	\decoRule
	\caption{Noise-intensity on $ \mu-0, \mu-10,\mu-20, \mu-30, \mu-40, \mu-50,$. Object Name: elephant-zun-lid.}
	\label{fig:noise-intensity}
\end{figure}

\subsection{Fit to PyTorch}
In order to save training time, we compress the dataset in PyTorch format. The structure of a single item is shown in Table \ref{tab:tensor-structure}.
\begin{table}[H]
	\caption{The structure of a single tensor in the dataset.}
	\label{tab:tensor-structure}
	\centering
	\begin{tabular}{l | l}
		\toprule
		\tabhead{Name} & \tabhead{Content} \\
		\midrule
		\multirow{3}{*}{input-tensor}  & Vertex \\  & Image \\  & Light Direction \\
		\hline
		\multirow{3}{*}{output-tensor}  & GT-Normal \\ & Image \\ & GT-Light-Direction \\
		\hline
		Light position & light position \\
		\hline 
		Camera Matrix  & K,R,t\\
		\hline 
		Depth Range  & minDepth, maxDepth\\
		\bottomrule
	\end{tabular}
\end{table}

>>>>

\section{Data Resources}
The object model we used are searched from internet.
A set of point cloud datasets for computer vision research has been published by \cite{data1}, \cite{data2}, \cite{data3} and \cite{data4}. These point clouds are scanned from real objects using high resolution scanners like Cyberware 3030 MS+ and calibrated with post processing. All objects has been scanned for hundreds of times with an exhaustive completion for the origin objects, which is up to millions points. (\cite{data1}). The dense point clouds make the normal inference task trivial since the neighbor based method performs adequately for this kind of task. Some of the point clouds even contain pre-computed normal maps based on more advanced methods. They all provide the accurate ground truth for the supervised learning method.

@@

	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/08.pergolesi-side-chair_texture.png}
		\caption{chair}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/42.zebra_texture.png}
		\caption{zebra}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test-dataset/01.bus_texture.png}
		\caption{bus}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test-dataset/03.baoshanlu_texture.png}
		\caption{baoshanlu}
	\end{subfigure}
	\decoRule
	\caption{Point clouds scanned by high resolution scanners}
	\label{fig:dataset-demo}
\end{figure}
Besides, some objects also have colored textures, as shown in the second row of Figure \ref{fig:dataset-demo}. This is specially prepared for the illuminated approach since they will take the image into account to evaluate the surface normal. By using textured models, our models become closer to the real dataset and have improved robustness, which can apply to the real dataset further.

\definecolor{direction-light-color}{RGB}{255,244,214}
\newcommand{\col}[1]{%
	\textcolor{#1}{\vrule width 0.5cm}}
\section{Synthesizing Scenes using Unity}
In order to simulate the data collection scenario close to the real world as much as possible. We did the following settings. A flat cylinder called $ stage $ is placed in the center of the 3D space as a platform to place objects. We fixed the stage in a predetermined position, which is not changed when images are captured. 
To provide ambient light, one directional light with RGB color FFF4D6 /col[direction-light-color] is placed in a top-view direction at a distance of 25 meters, which also has a fixed location.
An RGB-D camera is placed in a top-view direction around 10m away from the stage. The camera captures the depth map and the gray-scale image, which is randomly arranged after each scene. The moving range of the camera has 0.1m in both directions of the X, Y, and Z axis and a 1-degree random changed Euler angle. 
As an illumination light, a point light is placed around 5 meters away, which is also randomly moved after each scene. The moving range is 0.3m in both directions of the X, Y, and Z axis and 1 degree random in the Euler angle.

@@

\section{Data Preprocessing}
The raw data captured from Unity required further preprocessing before feeding them into the training models. 
\paragraph{Depth Map}
A depth map is captured by the depth camera in Unity, which is a 1 channel image that contains information relating to the Z-axis distance from object surface to the camera. It is saved as a 16-bit gray-scale image, i.e. each pixel in the range $\mathtt{0 - 65535}$.

The raw depth maps in real data that captured by light scanners usually have missing pixels. In order to fit well with real data, the synthetic data has been added uniform distributed noise, which randomly removes the valid pixels in the maps.
The simulated noise is distributed evenly around the whole map with specific noise intensity. A parameter $ \mu $ is used to control the intensity of noise. It denotes the $ \mu $-percent pixel drop-off. For example, $ \mu-10 $ removes 10\% pixels randomly. For each scene, the noise operation based on a random $ \mu $ in a range $ \left[0, 50\right]  $ is used. Some scenes have more missing pixels and some have fewer. The random noise intensity also enables the model to learn scenarios not only with noise but also with minor noise or even without noise.
Figure \ref{fig:noise-intensity} shows the noise effect with different $ \mu $.
%% add noise image
\begin{figure}[!h]
	\centering
	{\includegraphics[width=.9\textwidth]{./Figures/add_noise_depth.png}}
	\decoRule
	\caption{Noise-intensity on $ \mu-0, \mu-10,\mu-20, \mu-30, \mu-40, \mu-50,$. Object Name: elephant-zun-lid.}
	\label{fig:noise-intensity}
\end{figure}

The depth map is further converted to 3D vertex map after adding the noise.
\begin{figure}[h!]
	\centering
	\begin{tikzpicture} 
		% reference lines
		\draw[thick,dashed]	(0,0) -- (10,0) ; % bottom
		\draw[thick,dashed]	(0,3) -- (10,3) node[pos=0.9, above] {image plane}; % middle
		\draw[thick,dashed]	(0,6) -- (10,6); % top
		% camera 
		\filldraw[black] (5,0) circle (2pt) node[anchor=south west]{Camera Position};
		% world point 
		\filldraw[black] (7,6) circle (2pt) node[anchor=north west]{Point};
		% image point
		\filldraw[black] (6,3) circle (2pt) node[anchor=north west]{Pixel};
		% similiar triangles
		\draw[thick] (5,0) -- (5,6); % AB
		\draw[thick] (5,0) -- (7,6); % AC
		\draw[thick] (5,6) -- (7,6) node[midway, below] {$ X $}; % BC
		\draw[thick] (5,3) -- (6,3) node[midway, below] {$ u $};
		% measure arrows
		\draw[thick, <->] (4,0) -- (4,3) node[midway, left] {$ fk_u $};
		\draw[thick, <->] (3,0) -- (3,6) node[pos=0.3, left] {$ Z $};
	\end{tikzpicture}	
	\decoRule
	\caption{Convert depth to point in camera coordinate system}
	\label{fig:depth-triangulation}
\end{figure}

Consider a 3-dimensional Euclidean space. Use $ z $ axis to denote the depth. The $ x  $ and $ y $ axis are perpendicular to each other. For a pixel $ (u,v) $ on depth map, its depth $ D(u,v) $ is the $ Z $ component of the corresponding point $P_C = (X,Y,Z) $ regarding camera coordinate system. Knowing $ Z $, corresponding depth map pixel $ D(u,v) $ and the camera focal length in pixels $ fk_u, fk_v $, the other two component  $ X $ and $ Y $ in the 3D space can be calculated based on the triangle similarity.

\begin{dgroup*}

	\begin{dmath*}
		X = \frac{uZ}{fk_u}
	\end{dmath*}
	\begin{dmath*}
		Y = \frac{vZ}{fk_v}
	\end{dmath*}
\end{dgroup*}
Convert a point from camera coordinate system to the world coordinate system, using extrinsic matrix $ R $ and $ t $
\[P_W = P_CR+t \]

%% How to represent input tensor, to make it fast converse
The sizes of each training object are various, we normalized them to an unit scale thus they has relatively similar distance to the camera.
We showed the value fluctuation in each axis in Figure \ref{fig:data_range} before normalization. Table \ref{tab:data_range} gives a quantitative evaluation of the corresponding average values.

@@

\begin{dmath*}
	s = \max(X)-\min(X)
\end{dmath*}
which is calculated as the range of the $ X $ axis, but theoretically can be used by the $ Y $ or $ Z $ axes as well.

\begin{figure}[!h]
	\centering
	{\includegraphics[width=0.45\textwidth]{./Figures/Data_Extreme.png}}
	{\includegraphics[width=0.45\textwidth]{./Figures/Data_Range.png}}
	\decoRule
	\caption{Left: Extreme value in 3 axis; Right: Vertex range in 3 axis}
	\label{fig:data_range}
\end{figure}

\begin{table}[th]

	\centering
	\begin{tabular}{c | c c c}
		\toprule
		\tabhead{Axis} & \tabhead{Scale} & \tabhead{Min} & \tabhead{Max}\\
		\midrule
		X & 1.48 & -0.75 & 0.73\\
		\hline 
		Y & 1.56 & -0.76 & 0.80\\
		\hline 
		Z & 1.47 & 6.53 & 8.00\\
		\bottomrule
	\end{tabular}
	\caption{ The fluctuation of extreme values and their ranges in 100 random training items. }
	\label{tab:data_range}
\end{table}

\paragraph{Image}
The gray-scale image can be used for photometric stereo approach and also as a readable information for humans. Since the image captured by the camera is in RGB format, we need to convert it to gray colors to fit our models. It is based on the following equation.
\[ gray: \frac{R+2G+B}{4}  \]

\paragraph{Normal Map}
The normal map is the tangent surface normal, which is saved in a 8-bit/channel RGB image. The surface normal $ (n_x, n_y, n_z) $ and its corresponding RGB color $ (R,G,B) $ can be converted based on the following equation:
\begin{dgroup*}
	\begin{dmath*}
		n_x = \frac{R}{255} * 2 - 1
	\end{dmath*}
	\begin{dmath*}
		n_y = \frac{G}{255}*2 - 1
	\end{dmath*} 
	\begin{dmath*}
		n_z = 1-\frac{B}{255} * 2
	\end{dmath*}
\end{dgroup*}

In order to save training time, we compress the dataset in PyTorch format. The structure of a single item is shown in Table \ref{tab:tensor-structure}.
\begin{table}[H]
	\caption{The structure of a single tensor in the dataset.}
	\label{tab:tensor-structure}
	\centering
	\begin{tabular}{l | l}
		\toprule
		\tabhead{Name} & \tabhead{Content} \\
		\midrule
		\multirow{3}{*}{input-tensor}  & Vertex \\  & Image \\  & Light Direction \\
		\hline
		\multirow{3}{*}{output-tensor}  & GT-Normal \\ & Image \\ & GT-Light-Direction \\
		\hline
		Light position & light position \\
		\hline 
		Camera Matrix  & K,R,t\\
		\hline 
		Depth Range  & minDepth, maxDepth\\
		\bottomrule
	\end{tabular}
\end{table}
